On The Impact of Atoms of Confusion in JavaScript Code

### 2021-04-20 1_Introduction.tex
fix the introduction with correct numbers

To understand whether an atom of confusion introduces misunderstandings,
we surveyed 140 JavaScript developers. In the survey, 
their task was to predict the output of short code
snippets, with half of them containing atoms of confusion. 
{\color{red}The number of correct answers for the
  \emph{cleaned version} of the code snippets for seven (out of nine)
  atom candidates is at least 15\% higher than the corresponding
  \emph{confuse version}
  of the code snippet (i.e., with an atom candidate). The presence of an atom candidate
  might also affects the time necessary for submitting a correct answer.
  For instance, the presence of the Comma Operator atom increases
  the average time to predict the output by 65\%, though the output of snippets containing
  the Pre-Increment atom were correctly predicted 44\% faster.

>>>>

To understand whether an atom of confusion introduces misunderstandings,
we surveyed 140 JavaScript developers. In the survey, 
their task was to predict the output of short code
snippets, with half of them containing atoms of confusion. 
{\color{red}The number of correct answers for the
  \emph{cleaned version} of the code snippets for seven (out of nine)
  atom candidates is at least 10\% higher than the corresponding
  \emph{confuse version}
  of the code snippet (i.e., with an atom candidate). The presence of an atom candidate
  might also affects the time necessary for submitting a correct answer.
  For instance, the presence of the Comma Operator atom increases
  the average time to predict the output by 76.23\%, though the output of snippets containing
  the Pre-Increment atom were correctly predicted 38.19\% faster.
